Centralized Programming for Distributed Control Planes

### 2016-01-27 paper/introduction.tex
some tweaks

It is well-known that network configuration is highly error 
prone and that such errors can lead to costly network 
downtime~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish}.  
For instance, in the context of BGP, Mahajan~~\cite{mahajan+:bgp-misconfiguration} 
estimated that 200-1200 prefixes suffered from
misconfiguration each day and that close to 3 in 4 of all
new prefix advertisements were the result of misconfiguration.
Moreover, these misconfigurations sometimes cause significant network downtime for
individual networks~\cite{time-warner} or even broader internet connectivity problems~\cite{routing-instability,mahajan+:bgp-misconfiguration}.
\dpw{Note that \cite{time-warner} and I am not sure about the specifics of the problem there
or what exactly was misconfigured.  It is also unclear if our language really helps with the
``broader internet connectivity problems'' however, I thought that adding some specific examples
would help make the intro more compelling.  Feel free to rewrite.}

One reason is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
Another, more fundamental reason is the semantic mismatch between the intended high-level
policies and the low-level device-by-device configurations.  In particular,
many policies involve network-wide properties---prefer a certain neighbor,
never announce a particular destination externally, 
use a particular path only if another fails---but configurations describe the behavior of 
individual devices.
%
Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions satisfy the given high-level objectives.
%
Ensuring policy-compliance through this manual decomposition is challenging under normal
circumstances and even more so in the face of failures. Some decompositions that work correctly 
in failure-free environments, violate key constraints when failures occur.
%
As a result, many network configuration problems are only revealed after failures~\cite{batfish},
sometimes making a bad situation worse.

To reduce configuration errors, many practitioners have a adopted a template-based 
approach~\cite{x,y}, in which common configuration patterns are captured as parameterized templates.
 While templates help ensure certain kinds of consistency across several devices, they do not 
bridge the 
semantic divide between network policies and device-level configuration (\S\ref{sec:motivation}):
These templates do not provide new reasoning principles or fundamentally different abstractions 
from existing configuration languages.

Software-defined networking (SDN) and the abstractions
that support it are, in part, the research
community's response to the difficulty of maintaining policy
compliance through distributed interaction of individual
devices~\cite{sdn-languages}. Indeed, instead of organizing networks
around a distributed collection of devices that compute forwarding tables through
mutual interactions, the devices are told how to
forward packets by a centralized controller. The controller is responsible for ensuring that the
paths taken are compliant with operator specifications. 
%Researchers
%have developed increasingly sophisticated languages that let operators
%specify desirable network paths~\cite{x,y,z} which are then translated
%to forwarding tables at runtime.

>>>>

It is well-known that network configuration is highly error
prone and that such errors can lead to costly network
downtime~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish}.
For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.

%For instance, in the context of BGP, Mahajan~~\cite{mahajan+:bgp-misconfiguration}
%estimated that 200-1200 prefixes suffered from
%misconfiguration each day and that close to 3 in 4 of all
%new prefix advertisements were the result of misconfiguration.
%Moreover, these misconfigurations sometimes cause significant network downtime for
%individual networks~\cite{time-warner} or even broader internet connectivity problems~\cite{routing-instability,mahajan+:bgp-misconfiguration}.
%\dpw{Note that \cite{time-warner} and I am not sure about the specifics of the problem there
%or what exactly was misconfigured.  It is also unclear if our language really helps with the
%``broader internet connectivity problems'' however, I thought that adding some specific examples
%would help make the intro more compelling.  Feel free to rewrite.}

One reason for network configuration being onerous is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.

Another, more fundamental reason is the semantic mismatch between the intended high-level
policies and the low-level device-by-device configurations.  In particular,
many policies involve network-wide properties---prefer a certain neighbor,
never announce a particular destination externally,
use a particular path only if another fails---but configurations describe the behavior of
individual devices.
%
Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions satisfy the high-level objectives.
%
Ensuring policy-compliance through this manual decomposition is challenging under normal
circumstances and even more so in the face of failures. Some decompositions that work correctly
in failure-free environments, violate key constraints when failures occur.
%
As a result, many network configuration problems are only revealed after failures~\cite{batfish},
sometimes making a bad situation worse.

To reduce configuration errors, many practitioners have a adopted a template-based
approach~\cite{hatch,thwack}, in which common configuration patterns are captured as parameterized templates.
 While templates help ensure certain kinds of consistency across devices, they do not
bridge the
semantic divide between network policies and device-level configuration.
They do not provide fundamentally different abstractions
from existing configuration languages.

Software-defined networking (SDN) and its abstractions 
are, in part, the research
community's response to the difficulty of maintaining policy
compliance through distributed interaction of individual
devices~\cite{sdn-languages}. Indeed, instead of organizing networks
around a distributed collection of devices that compute forwarding tables through
mutual interactions, the devices are told how to
forward packets by a centralized controller. The controller is responsible for ensuring that the
paths taken are compliant with operator specifications.
%Researchers
%have developed increasingly sophisticated languages that let operators
%specify desirable network paths~\cite{x,y,z} which are then translated
%to forwarding tables at runtime.
